\documentclass[11pt]{article} % Document type
\usepackage{graphicx}
\usepackage{float}
\usepackage{geometry}
\geometry{legalpaper, margin=1in}
\title{Assignment 4}
\author{Michael Kamensky}
\date{\today} % Sets the date to \today, or any date you specify
\begin{document}\maketitle % Start the document
\section{What I learned}
For this assignment:
\begin{itemize}
\item I learned how to work with matrices in C.
\item I learned that a matrix in C is a pointer of an array which points to more arrays. The first array represent the rows and the second arrays represent the cols.
Additionally, I learned how to clear the array by first clearing the cols arrays and then clear the row array of pointers to make sure that there are no memory leaks.
\item I learned how to work with fscanf and how you can use format string to read the values from files that you need for your project.
\item I worked with fopen and fclose and other file commands and learned how they work, learned that I need to close files.
\item I learned how to write into files for output.
\item To work with stdout and stdin I learned there is no need to open or close anyfiles.
\item I found out that gcc compiler in some cases finds errors that clang doesn't. Maybe it is a good idea to use both compilers to catch maximum number of errors.
\item In c I learned that in some programs you can work with structures without its definition. As long as a pointer to the structure is used and accessor functions are used.
\item Learned new case with getopt on how to take strings as an argument.
\item Finally I learned how to work with the ncurses libary and was able to create a display for the game of life.
\end{itemize}
\end{document}
